### 2015-02-18 fundamentals/impl.tex
using the glossary

The information-gathering step begins by polling potential consumers. Agents
denote both the quantity of a commodity they need to consume as well as the
target isotopics, or quality, by posting their demand to the market exchange as
a series of \textit{requests}. An optional collection of demand constraints are
associated with each collection of requests. Collections of requests may be
grouped together, denoting \textit{mutual} requests that represent demand for
some common purpose. For example, a reactor may request UOX and MOX fuel
mutually, indicating that either will satisfy its demand for fuel.

Suppliers then respond to the series of requests with a \textit{bid}. A bid
supplies a notion of the quantity and quality of a resource to match a
request. Suppliers may add an arbitrary number of constraints to accompany
bids. For example, an enriched UOX supplier may supply both a natural Uranium
and SWU constraint. Any potential resource transfer may be denoted as
\textit{exclusive}. An exclusive transfer must either be met fully or not at all
in order to support concepts such as the trading of individual reactor
assemblies.

>>>>

The information-gathering step begins by polling potential consumers. Agents
denote both the quantity of a commodity they need to consume as well as the
target isotopics, or quality, by posting their demand to the market exchange as
a series of \textit{requests}. An optional collection of demand constraints are
associated with each collection of requests. Collections of requests may be
grouped together, denoting \textit{mutual} requests that represent demand for
some common purpose. For example, a reactor may request \gls{UOX} and \gls{MOX} fuel
mutually, indicating that either will satisfy its demand for fuel.

Suppliers then respond to the series of requests with a \textit{bid}. A bid
supplies a notion of the quantity and quality of a resource to match a
request. Suppliers may add an arbitrary number of constraints to accompany
bids. For example, an enriched \gls{UOX} supplier may supply both a natural Uranium
and SWU constraint. Any potential resource transfer may be denoted as
\textit{exclusive}. An exclusive transfer must either be met fully or not at all
in order to support concepts such as the trading of individual reactor
assemblies.
